---
title: "Capstone ver1"
author: "J-Kader"
date: "Saturday, November 07, 2015"
output: html_document
---
# Ponpare Coupons

Ponpare is Japanese coupon site that offers discount coupons on many activities, goods and services. The goal of the followng analysis and model is to improve Ponpare recommendation system 

We have few datasets provided by the company that give us information about the users and the coupons purchased.

```{r, echo=FALSE}
user_list_en = read.csv("C:/Users/JKADER/Documents/coupons/user_list_en.csv")
```


## Descriptive Aspect

** USERS**

  >*Who are our Users? and what do we know about them?*

let us have a look at the *users list* to see the distribution of the **AGE** of the users.

```{r}
str(user_list_en)
```
We have 22,875 observations and 7 variables including AGE, SEX ID(Gender), USER ID hash, PREF NAME (which is the name of the user's area in Japenese), en pref name (the English translation of the PREF NAME), Registered date and Withdrawal date (dates of the user registration and withdrawal from the website). 

for my analysis, I will only be using Age, Sex_id, prefecture name and the User ID.
Now, let us explore Age.
```{r}
hist(user_list_en$AGE, main="Age Distribution", sub="Figure 1",cex.sub=0.7, col="blue", xlab= "USERS AGE")

```

Figure (1) shows that the *AGE* variable has a normal distribution 

```{r include=FALSE}
require(Hmisc)
```
```{r}
describe(user_list_en$AGE)
```

We have 66 different ages category, our users' age varies between 15 to 80 with a mean of 42.5 years and standard deviation of 11.84.

I categorized age based on 10 years interval and called the new variable *age group* 

```{r}
attach(user_list_en)
user_list_en$age_group[AGE<=19 & AGE>=15] = "18"
user_list_en$age_group[AGE<=29 & AGE>=20] = "20"
user_list_en$age_group[AGE<=39 & AGE>=30] = "30"
user_list_en$age_group[AGE<=49 & AGE>=40] = "40"
user_list_en$age_group[AGE<=59 & AGE>=50] = "50"
user_list_en$age_group[AGE<=69 & AGE>=60] = "60"
user_list_en$age_group[AGE<=79 & AGE>=70] = "70"
user_list_en$age_group[AGE<=89 & AGE>=80] = "80"
user_list_en$age_group=as.numeric(user_list_en$age_group)
hist(user_list_en$age_group, main="Age Group Distribution", col="yellow",sub="Figure 2", cex.sub=0.7, xlab="Age Group")

```


By creating age groups to categorize users, I was able to determine that most users are in their 30's and 40's; 
* 30% of users are in their 30's
* 28% of users in their 40's and 
* 18% of users in their 50's

This could be explained by the fact that young USERS in these age groups are more net-savvy and use on-line shopping more frequently than the older less tech-savvy age groups. 
    
Now that we know the age, Let us explore our USERS's **GENDER**.    

```{r}
describe(user_list_en$SEX_ID)
```

The results show that we slightly have more MALE users that make up  52% of our entire users.

  > *Does the gender of users change in differnt age groups? Are there more males than females in some age groups or vise versa?*

Let us calculate the probabilities of **Gender** per **Age** category.

```{r}
t= table(user_list_en$SEX_ID,user_list_en$age_group)
barplot(prop.table(t,2), legend=paste(unique(user_list_en$SEX_ID)), ylab="Probability", xlab="Group Age", main="Gender & Age Group", sub="Figure 3", cex.sub=0.7, col=c("pink","skyblue"))
```

Figure (3) shows that in the (20, 30 and 40) age groups we almost have equal gender presence, with slightly more females than males.

Interestingly, the genders of users start shifting slightly in the 50's age group, with a drastic shift in the 60's age group where males make up 70% of users,  and in the 70's age group where males increase to 80% of users in this age group, this could be due to the traditional role of men in Japan. 

Let us look at the **AREA** were our users come from and determine the distribution of our users based on the prefecture name.

```{r}
unique(user_list_en$en_pref_name)
```

Our users are distributed over 47 prefectures. 

  > *Are our users clustered in some prefecture more than other prefecture?*

```{r warning=FALSE}
barplot(table(user_list_en$en_pref_name), name.arg=row.names(user_list_en),main ="Prefecture Distribution\n Figure 4", las=2, cex.names=0.6, space=NULL, col="blue")
```


Figure 4, shows the distribution of users in the 47 Prefectures where Tokyo (with 2830 = 12% of users), Kanagawa and Osaka (with 7% of users) have the most users and Tottori Prefecture where we have the least users with only 25 users. However, I have 7256 missing values, which could change this finding. 

**COUPONS**

Now let us look at the attributes of the product that Ponpare offers our users **The Coupons**. 

Ponpare provided us with three datasets with many variables about the coupons, the first dataset is called "*coupon_detail_train_en*" which includes "Item Count" (count of coupons at each purchase), "small area" (geographical/location), "Coupon ID", "User ID", and "Purchased ID" (log of the purchase transactions). 


```{r echo=FALSE}
coupon_detail_train_en = read.csv("C:/Users/JKADER/Documents/coupons/coupon_detail_train_en.csv")
```


```{r}
 str(coupon_detail_train_en)
```

We have 168,996 observations in this dataset based on "Purchase ID", we have 22,782 unique "Coupon ID" and 19,368 unique "User ID". 

The second dataset is called *Coupon_list_train_en* which also includes many details about the coupons

```{r echo=FALSE}
coupon_list_train_en = read.csv("C:/Users/JKADER/Documents/coupons/coupon_list_train_en.csv")
```


```{r}
str(coupon_list_train_en)
```

This dataset has 19,413 observations based on unique "coupon ID" with 29 variables including "large area" (geographical/location), "ken name" (another name for prefecture), "genre", "capsule name" (geographical/location),"price rate" (discount rate),"catalogue price", "discount price" (price after discount), "desp from", "disp end" ,"disp period" (dates of the dispensed coupon), "valid from", "valid end", "valid period" (coupons validity dates), "usable dates" (some coupons are usable on certain days), 


To create a comprehensive dataset that includes all variables for Coupons, we need to merge the two datasets

```{r}
cpdtr = coupon_detail_train_en
cpltr= coupon_list_train_en
train <- merge(cpdtr,cpltr)
```
```{r}
names(train)
```

I need to clean up some of the variables that I will exclude from our analysis. I will only include the following variables:

```{r}
train <- train[,c("COUPON_ID_hash","USER_ID_hash","en_genre","DISCOUNT_PRICE","PRICE_RATE","USABLE_DATE_MON","USABLE_DATE_TUE","USABLE_DATE_WED","USABLE_DATE_THU","USABLE_DATE_FRI","USABLE_DATE_SAT","USABLE_DATE_SUN","USABLE_DATE_HOLIDAY","USABLE_DATE_BEFORE_HOLIDAY","en_large_area", "en_ken","en_small_area","ITEM_COUNT")]
```
```{r}
str(train)
```

Now let us merge the resulted dataset that contains all coupons variables with our *"users"* dataset to create a dataset that contains all users and coupons. This dataset will help us understand realtions between users and the type of coupons. 

```{r}
users <-user_list_en[,c("SEX_ID","AGE","USER_ID_hash","age_group")]
train.2 <- merge(train, users)
```

The result of merging the previous datasets is a new dataset that has 19,368 "unique coupon ID" and 22,782 "unique users" with 21 variables. 

Let us explore some of them.

  >*Is there a coupon genre that is more popular than another? let us see which coupons our users purchased the most?*

```{r}
plot(train.2$en_genre, train.2$ITEM_COUNT, las=2,cex.names=0.2, cex.axis=0.7, main="Coupon Genre & Item Count", sub="Figue 5",cex.sub=0.7 )
```

We can determine from (Figure 5) that among the 13 genres we have, users puchased coupons in the "Food" genre in big counts, where some users purchased 10 or more coupons at a time, followed by "other coupons" (not clear abot what other coupons genre is), "Delivery Services", "Hotels" and "Leisure".

  >*But if users buy more than 10 or 20 coupons at a time in a specific genre, does that mean that this genre the the most popular?*
  
 
```{r}
describe(train.2$en_genre)
```

Looking at the results above we conclude that the "Food" genre is the most popular which makes up 36% of the puchased coupons, followed by "other coupons" and then "Delivery Service". 

Therefore, this confirms that the "Food" genre is the most popular.

  >*Do female users and male users share the same preference in genres?*
  
  
```{r include=FALSE}
require(ggplot2)

```


```{r}
GG=ggplot(train.2, aes(x=en_genre, fill=SEX_ID)) + geom_histogram(binwidth=.5, alpha=.5, position="identity") +theme(axis.text.x = element_text(face="plain", color="#993333", size=9, angle=90))
GG+ggtitle("Gendre & Genre")
```


From the figure above, we find that some genres are more popular with females than males, such as beauty salons, spas and delivery service. However, Food and hotel coupons are more popular with males.

  >*Does the **Discount Rate** of the coupons matter?*

Let us plot the price rate (discount rate), but before that I will recode our (Price Rate) to intervals of 5's. i will focus on price rate 30 and above, since there were very few coupons that were sold under this rate.

  >*Does the different "usable day" of the coupon makes some coupons more popular?*
  
variables with the (usable date) consist of three values (0,1 and 2),  if we assume number(2) means certain kind of coupons with certain conditions, number (1) means usable that day and number(0) means not usable that day, we come up with the following  findings after looking at each "usable day":

Coupons usability coded with number (2) were not purchased widely during the week (Mon, Tue, Wed, Thu and on holidays), but the purchase of these coupons increased on Friday and Sunday and very notably increased on Saturday and before the holiday.

After looking at the frequency of Coupons usability coded with number (1), i found that the usablitiy on different days of the week does not make a significant difference on the purchase. All coupons with different usable dates were purchased similarly, except for the slight decrease on coupons "usable Saturday" which could be explained with the spike in purchases of coupons type (2) usable Saturdays

Monday
```{r echo=FALSE}
table(train.2$USABLE_DATE_MON)

```
Tuesday
```{r echo=FALSE}
table(train.2$USABLE_DATE_TUE)
```
Friday
```{r echo=FALSE}
table(train.2$USABLE_DATE_FRI)
```
Sat
```{r echo=FALSE}
table(train.2$USABLE_DATE_SAT)
```


```{r echo=FALSE}
attach(train.2)

```
```{r}
train.2$Discount_Rate[PRICE_RATE<=19 & PRICE_RATE>=0]= "15"
train.2$Discount_Rate[PRICE_RATE<=29 & PRICE_RATE>=20]= "20"
train.2$Discount_Rate[PRICE_RATE=30]= "30"
train.2$Discount_Rate[PRICE_RATE<=35 & PRICE_RATE>30]= "35"
train.2$Discount_Rate[PRICE_RATE<=40 & PRICE_RATE>=36]= "40"
train.2$Discount_Rate[PRICE_RATE<=45 & PRICE_RATE>=41]= "45"
train.2$Discount_Rate[PRICE_RATE<=50 & PRICE_RATE>=46]= "50"
train.2$Discount_Rate[PRICE_RATE<=55 & PRICE_RATE>=51]= "55"
train.2$Discount_Rate[PRICE_RATE<=60 & PRICE_RATE>=56]= "60"
train.2$Discount_Rate[PRICE_RATE<=65 & PRICE_RATE>=61]= "65"
train.2$Discount_Rate[PRICE_RATE<=70 & PRICE_RATE>=66]= "70"
train.2$Discount_Rate[PRICE_RATE<=75 & PRICE_RATE>=71]= "75"
train.2$Discount_Rate[PRICE_RATE<=80 & PRICE_RATE>=76]= "80"
train.2$Discount_Rate[PRICE_RATE<=85 & PRICE_RATE>=81]= "85"
train.2$Discount_Rate[PRICE_RATE<=90 & PRICE_RATE>=86]= "90"
train.2$Discount_Rate[PRICE_RATE<=95 & PRICE_RATE>=91]= "95"
train.2$Discount_Rate[PRICE_RATE<=100 & PRICE_RATE>=96]= "100"

```

```{r}
train.2$Discount_Rate=as.numeric(train.2$Discount_Rate)
hist(train.2$Discount_Rate, main="Price Rate Distribution", col="Red", sub="Figure 6", cex.sub=0.7, xlab="Discount Rate")
```

From Figure 6, we can clearly see the popularity of the (50%) discount rate with the highest frequency, followed by discount rate (55%) and (80%) 

## Inferential Aspect

In the next step, I did some inferntial analysis to find the effect of explanatory variables on Price Rate, for this purpose I used a linear regression model.

First I tested the effect of GENDER on Price Rate

```{r}
attach(train.2)
price.gender = lm(Discount_Rate~SEX_ID)
summary(price.gender)
```

From the univariate regression model (price.gender), I found that the effect of gender on price rate is significant (P < 0.05), which means males seek cheaper price rate (with a negative change).


Now let me show the effect of AGE on Price Rate

```{r}
price.age = lm(Discount_Rate~AGE)
summary(price.age)
```

From the univariate regression model (price.age) to test the effect of age on price rate, we realize that each year increase in age causes a decrease in price rate by 1.17.

How about AREA? I also analyzed the effect of large area on price rate and found that 6 out of the 9 have significant effect on price rate 

```{r}
price.area = lm(Discount_Rate~en_large_area)
summary(price.area)
```


Now, let us test the effect of AGE and GENDER on price rate in a multiple linear regression to test the effect of each variable adjusted by the other.

```{r}
price.age.gender = lm(Discount_Rate~AGE+SEX_ID)
summary(price.age.gender)
```

In this model we find that the effects of both sex and age are significant on price rate, but after control for age the effect of sex decreased. 


  >*But do other variables have an effect on the purchase transaction (YES purchase = 1, NO purchase = 0) of the coupon?*
  
Ponpare provided us with a huge dataset *coupon visit train* that contains the viewing logs for every visit a User made during a period of time that spans from 2011-07-01 to 2012-06-23. This dataset has 2,833,180 observations with 8 variables, which makes it a very large dataset to work with. 

The variable of interest in this dataset is (Purchase Flag) which records whether the user purchased a coupon (value "1") or did not purchase the coupon (value "0") for every visit.

The other variables describe more details about each user's visit to the website "I DATE" (date of the visit), "PAGE SERIAL", "REFERRER hash", "COUPON ID hash","USER ID hash", "SESSION ID hash","PURCHASEID hash" (record of the purchase transaction).I will not use these variables in my analysis.

To create a more manageable dataset, I substracted a smaller dataset from the *coupon visit train*, I subset it based on a period of a week (May 13,2013 to 19,2013), then I merged the week dataset with the other dataset (which contains all variables of coupons and users), I did the merge based on the unique (coupon ID hash).

```{r echo=FALSE}
train.W1 = read.csv("C:/Users/JKADER/Documents/coupons/train.W1.csv")
```
```{r}
str(train.W1)
```

Now that we have a variable with a binary value, let us run a logeistic regression to see if our variables have an effect on this response variable.

We will start with GENDER.

```{r}
log.gender=glm(PURCHASE_FLG~SEX_ID, train.W1, family="binomial")
summary(log.gender)
```


We can see that the slope for sex is negative (female is the reference group), meaning that the probability of event (PURCHASE_FLG) is higher for females.

Now let us test for AGE

```{r}
log.age=glm(PURCHASE_FLG~AGE, train.W1, family="binomial")
summary(log.age)
```

The p value is not significant so the probability of PURCHASE FLG does not relate to the age.

  

```{r include=FALSE}
require(plyr)
```
```{r}
y = count(train.2, "USER_ID_hash")
```
```{r}
train.3 = merge(train.2, y)
train.4 = train.3[order(train.3$freq),]
train.5 = subset(train.4, !duplicated(train.4$USER_ID_hash))
```
```{r}
sample.1=tail(train.5,100)
```

Now that we have the frequency of the users as a variable, let us test if Gender and Age have an effect on determining how frequent

```{r}
reg.freq=lm(freq~AGE + SEX_ID, sample.1)
summary(reg.freq)
```

From the result of the regression we can see that male users are more frequent users than females with 1.35 males to 1 females after controling the age. 

```{r}
sample.2 = sample.1
sample.2[is.na(sample.2)]<- 1
unique(is.na(sample.2))
sample.3 = sample.2[,-c(1,2,5,17,21)]
```

```{r}
y.2=y[order(y$freq),]
freq.user=tail(y.2,100)
sample.6=merge(freq.user, train.2)
```

```{r}
sample.7=sample.6[,c(4,5,6,7,8,9,10,11,12,13,14,15,17,20,22)]
```

```{r}
sample.8 = sample.7
sample.8[is.na(sample.8)]<-1
```
```{r include=FALSE}
require(car)
```
```{r}
attach(sample.8)
en_genre_recode = recode(en_genre, "c('Beauty', 'Nail and eye salon') = 'Beauty';c('Delivery service')='Delivery service';c('Food')='Food';c('Lesson','Health and medical','Other coupon')='Other coupon';c('Spa','Relaxation')='Spa Relaxation';c('Hotel and Japenese hotel')='Hotel and Japenese hotel';c('Leisure')='Leisure';c('Hair salon')='Hair salon'")
sample.9=cbind(sample.8, en_genre_recode)
sample.9[is.na(sample.9)]<-1
```
```{r}
sample.10=sample.9
sample.10$en_genre = Null
```
```{r}
sample.11 = sample.10[,-c(3:11)]
```

```{r}
sample.11[,"dummy"]=1
sample.12=as.data.frame(model.matrix(dummy~.,sample.11))
sample.12[,1]=NULL
```

```{r}
rn_train <- sample(nrow(sample.12),floor(nrow(sample.12)*0.7))
sample.12.train<-sample.12[rn_train,]
sample.12.test<-sample.12[-rn_train,]
```
```{r}
KMC = kmeans(sample.12.train, centers=10, iter.max=1000)
```
```{r}
KMC.kcca = as.kcca(KMC,sample.12.train)
user.clustors = predict(KMC.kcca, newdata=sample.12.test)
```
```{r}
train.validation = cbind(sample.12.train, KMC$cluster)
test.validation = cbind(sample.12.test, user.clustors)
```
```{r}
View(train.validation[KMC$cluster==1,])
```


```{r}
daisy.mat.train <- daisy(sample.11.train, metric="gower")
```

